Concurrent Programming with CXL

### 2020-06-15 book/paper.tex
Starting on bibliography

\documentclass{report}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{framed}
\usepackage{tcolorbox}
\usepackage{verbatim}
\usepackage{fancyvrb}
\usepackage{comment}
\usepackage{amsmath}

@@

CXL is heavily influenced by Leslie Lamport's work on
TLA+, TLC, and PlusCal~\cite{}.
CXL is designed to have a lower learning curve than those
systems, but is not as powerful.  When you finish this book
and want to learn more, we strongly encourage checking
those out.
Another excellent resource is Fred Schneider's book ``On
Concurrent Programming.''

@@

What we want is a special kind of lock that allows either one writer
or one or more readers to be in the critical section.  This is called
a \emph{reader/writer lock}~\cite{courtois71}.
We will explore various ways of implementing reader/writer locks in
this chapter and future ones.

@@

In the late 70s, Xerox PARC developed a new programming language called
Mesa~\cite{mesa}.
Mesa introduced various important concepts to programming languages,
including software exceptions and incremental compilation.  Mesa also
incorporated a version of monitors.
However, there are some subtle but important differences with Hoare
monitors that make Mesa monitors quite unlike split binary semaphores.

@@

The code in Figure~\ref{fig:hw} is based on code developed by Herlihy and
Wing~\cite{HW}.
The code is a ``proof of existence'' for non-blocking synchronization; it
is not necessarily practical.
There are two variables.  \texttt{items} is an unbounded array with each
entry initialized to \texttt{()}.  \texttt{back} is an index into the
array and points to the next slot where a new value is inserted.
The code uses two interlock instructions:
\begin{itemize}
\item \texttt{inc(p)}: atomically increments \texttt{\^{}p} and returns
the old value;
\item \texttt{swap(p)}: sets \texttt{\^{}p} to \texttt{()} and returns
the old value.
\end{itemize}

@@

>>>>

\documentclass{report}
\usepackage{fullpage}
\usepackage[nottoc,numbib]{tocbibind}
\usepackage{graphicx}
\usepackage{framed}
\usepackage{tcolorbox}
\usepackage{verbatim}
\usepackage{fancyvrb}
\usepackage{comment}
\usepackage{amsmath}

@@

CXL is heavily influenced by Leslie Lamport's work on
TLA+, TLC, and PlusCal~\cite{Lamport02, Lamport09}.
CXL is designed to have a lower learning curve than those
systems, but is not as powerful.  When you finish this book
and want to learn more, we strongly encourage checking
those out.
Another excellent resource is Fred Schneider's book ``On
Concurrent Programming''~\cite{Schneider97}.

@@

What we want is a special kind of lock that allows either one writer
or one or more readers to be in the critical section.  This is called
a \emph{reader/writer lock}~\cite{CHP71}.
We will explore various ways of implementing reader/writer locks in
this chapter and future ones.

@@

In the late 70s, Xerox PARC developed a new programming language called
Mesa~\cite{LR80}.
Mesa introduced various important concepts to programming languages,
including software exceptions and incremental compilation.  Mesa also
incorporated a version of monitors.
However, there are some subtle but important differences with Hoare
monitors that make Mesa monitors quite unlike split binary semaphores.

@@

The code in Figure~\ref{fig:hw} is based on code developed by Herlihy and
Wing~\cite{HW87}.
The code is a ``proof of existence'' for non-blocking synchronization; it
is not necessarily practical.
There are two variables.  \texttt{items} is an unbounded array with each
entry initialized to \texttt{()}.  \texttt{back} is an index into the
array and points to the next slot where a new value is inserted.
The code uses two interlock instructions:
\begin{itemize}
\item \texttt{inc(p)}: atomically increments \texttt{\^{}p} and returns
the old value;
\item \texttt{swap(p)}: sets \texttt{\^{}p} to \texttt{()} and returns
the old value.
\end{itemize}

@@

\bibliographystyle{alpha}
\bibliography{paper}
